Maximizing Ink in Symmetric Partial Edge Drawings of $k$-plane Graphs

### 2018-02-14 eurocg/paper.tex
Added small section at the end of Hardness proof, explaining the extension to Bruckdorfers proof

%\renewcommand\windowpagestuff{%
%	\includegraphics{Reduction_visual}
%	\captionof{figure}{Example of three variable gadgets and\\ a satisfied clause gadget. Dotted parts do not belong\\ to the SPED.}
%	\label{fig:gadget_connection}
%}
%\opencutleft
\begin{proof}
%		\begin{cutout}{2}{0pt}{0.44\textwidth}{15}
	We reduce from the \NP-hard problem \ppsat~\cite{l-pftu-82} using similar ideas as in Bruckdorfer's general proof of the hardness of \maxsped~\cite{b-sgh-15}. %, which reduces from the more restricted problem \textsc{Planar Positive 1-in-3 Sat}. 
	Let $\phi$ be a planar 3-Sat formula with $n$ variables $\{x_1, \dots, x_n\}$ and $m$ clauses $\{c_1, \dots, c_m\}$, each consisting of three literals.
	We can assume that $\phi$ comes with a planar drawing of its variable-clause graph $H_\phi$, which has a vertex for each variable $x_i$ and a vertex for each clause $c_j$.
	Each clause vertex is connected to the three variables appearing in the clause.
	In the drawing of $H_\phi$ all variable vertices are placed on a horizontal line and the clause vertices connect to the adjacent variable vertices either from above or from below the horizontal line.
	In our gadget-based reduction we mimic the drawing of $H_\phi$ by creating a 3-plane drawing $\Gamma_\phi$ as a set of line segments of uniform length and a value $L$ such that $\Gamma_\phi$ has a SPED with ink at least $L$ if and only if $\phi$ is satisfiable.
	Figure~\ref{fig:gadget_connection} shows a sketch of the gadgets.
%		\end{cutout}

@@

>>>>

%\renewcommand\windowpagestuff{%
%	\includegraphics{Reduction_visual}
%	\captionof{figure}{Example of three variable gadgets and\\ a satisfied clause gadget. Dotted parts do not belong\\ to the SPED.}
%	\label{fig:gadget_connection}
%}
%\opencutleft
\begin{proof}
%		\begin{cutout}{2}{0pt}{0.44\textwidth}{15}
	We reduce from the \NP-hard problem \ppsat~\cite{l-pftu-82} using similar ideas as in Bruckdorfer's general proof\textcolor{blue}{-sketch} of the hardness of \maxsped~\cite{b-sgh-15}. %, which reduces from the more restricted problem \textsc{Planar Positive 1-in-3 Sat}. 
	Let $\phi$ be a planar 3-Sat formula with $n$ variables $\{x_1, \dots, x_n\}$ and $m$ clauses $\{c_1, \dots, c_m\}$, each consisting of three literals.
	We can assume that $\phi$ comes with a planar drawing of its variable-clause graph $H_\phi$, which has a vertex for each variable $x_i$ and a vertex for each clause $c_j$.
	Each clause vertex is connected to the three variables appearing in the clause.
	In the drawing of $H_\phi$ all variable vertices are placed on a horizontal line and the clause vertices connect to the adjacent variable vertices either from above or from below the horizontal line.
	In our gadget-based reduction we mimic the drawing of $H_\phi$ by creating a 3-plane drawing $\Gamma_\phi$ as a set of line segments of uniform length and a value $L$ such that $\Gamma_\phi$ has a SPED with ink at least $L$ if and only if $\phi$ is satisfiable.
	Figure~\ref{fig:gadget_connection} shows a sketch of the gadgets.
%		\end{cutout}

@@

\textcolor{blue}{We extended Bruckdorfers proof-sketch by giving the ink contributions of each part of $\Gamma_\phi$, in order to give an ink value $L$ that can be achieved if and only if $\phi$ is satisfiable. Further we changed the variable gadgets to cycles of edge pairs, partly to guarantee, that the gadgets have the same ink value regardless of their corresponding truth values and partly for aesthetic reasons. And finally we changed the clause gadgets from three edges intersecting in the same point to the described triangles in order to achieve general position.}
